Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-05-09 main.tex
Updates from Overleaf

%ground truth Y (e.x. patient's survival):\\[0.5cm]
$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
% natural exponential function => y=e^x
\end{flushleft}
%Y$:
%$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
%\linebreak
%\linebreak
where,\\
\begin{outline} % for highlight
\1 t represents the survival time
\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$)
\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
\1 the term $h_0$ is called the baseline hazard. It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1). The ‘t’ in $h(t)$ indicates us that the hazard may vary over time

\end{outline}

Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
\\[0.5cm]
Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
%A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
%Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
%$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
%\linebreak
%(predicted Y, output) intercept, slope, independent (input) \Times
%\end{math}

Thus, the biomarker discovery strategy is survival modeling through collections of $X_1...X_n$ features from cancer datasets.\\[1cm]

Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the OS.

>>>>

%ground truth Y (e.x. patient's survival):\\[0.5cm]
$h(t) = h_0(t) \times exp(\beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n)$\\[0.3cm]
% natural exponential function => y=e^x
\end{flushleft}
%Y$:
%$Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n + \epsilon$
%\linebreak
%\linebreak
where,\\
\begin{outline} % for highlight
\1 t represents the survival time
\1 $h(t)$ is the hazard function determined by a set of n covariates ($X_1...X_n$, e.g. clinicopathological features: such as age, gender, gene expression, cancer stage, smoking, alcohol, or even spiritual, emotional, and social status)
\1 the coefficients ($\beta_1...\beta_n$) measure the impact (i.e., the effect size) of covariates
\1 the term $h_0$ is called the baseline hazard. It corresponds to the value of the hazard if all the $X_i$ are equal to zero (the quantity exp(0) equals 1). The ‘t’ in $h(t)$ indicates the hazard may vary over time
\end{outline}

%Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage, or even spiritual, emotional, and social status)
%\\[0.5cm]
%Coefficients $\beta_0...\beta_n$ (built in model)\\[0.5cm]
%A residual (error) term is calculated as $\epsilon=Y - \hat Y$\\
%Since the model established by survival analysis, predicted value $\hat Y$ is calculated as:\\[0.3cm]
%$\hat Y = \beta_0 + \beta_1 X_1 + \beta_2 X_2 + \beta_3 X_3 + ... + \beta_n X_n$
%\linebreak
%(predicted Y, output) intercept, slope, independent (input) \Times
%\end{math}
Thus, the biomarker discovery strategy is survival modeling through collection of $X_1...X_n$ features from cancer datasets.\\[1cm]

Univariate and multivariate Cox proportional regression model\cite{Andersen1982}, using the "coxph" function in R package "survival", was applied to calculate hazard ratio, \acrfull{ci95} and its significance, and to estimate the independent contributions of each clinicopathological features to the overall survival (OS).
